Software Citation Principles

### 2016-07-23 sc-principles/software-citation-principles.tex
minor wording edit

Some of the most actionable work has come from the UK Software Sustainability
Institute (SSI) in the form of blog posts written by their community fellows:

In a blog post from 2012, Jackson discusses some of the pitfalls of trying to
cite software in publications~\cite{ssi-how-to-cite}. He includes useful
guidance for when to consider citing software as well as some ways to help
``convince'' journal editors to allow the inclusion of software citations.

>>>>

Some of the most actionable work has come from the UK Software Sustainability
Institute (SSI) in the form of blog posts written by their community fellows.
For examplel, in a blog post from 2012, Jackson discusses some of the pitfalls
of trying to cite software in publications~\cite{ssi-how-to-cite}. He includes
useful guidance for when to consider citing software as well as some ways to help
``convince'' journal editors to allow the inclusion of software citations.
